---
title: "survival"
author: "YJ"
date: "August 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
P values are calculated 
```{r data processing}
library(tidyverse)
dir<-file.path("C:/Users/My computer/Dropbox/CSHL/R/SMN_amniotic_injection")
km<-read_csv(file.path(dir,"Kaplan-Meier_analysis.csv"))
pvals<-filter(km, Category == "P value")
grep("<",pvals$values) # find which ones have "<"
pvals$values<-as.numeric(sub("< ","", pvals$values)) # find which ones have "< " and remove it

pvals<- pvals %>% mutate(p.adj = round(p.adjust(pvals$values,"BH"),6), signif = p.adjust(pvals$values,"BH")<0.05) # test which pvals are FDR<0.05

pvals %>% mutate(p.adj = round(p.adjust(pvals$values,"bonferroni"),6), signif = p.adjust(pvals$values,"bonferroni")<0.05)

pvals<-pvals%>%mutate(comparisons = paste(pvals$ASO1, "vs.", pvals$ASO2))
pvals[,c("comparisons", "Tests", "values","p.adj")]
```
Which comparison pairs are signficant?
```{r finally summarize which comparisons are significant}
table(pvals$comparisons, pvals$signif)
```
Look at tests separately
```{r}
table(pvals$comparisons, pvals$signif, pvals$Tests)
```

Cox Proportional hazard analysis (http://www.sthda.com/english/wiki/cox-proportional-hazards-model)
(https://cran.r-project.org/web/packages/survivalAnalysis/vignettes/multivariate.html)
first, install the necessary packages
install.packages(c("survival", "survminer"))

Load the packages
```{r}
library(survival)
library(survminer)
```
load the data sets and set treatment levels
```{r}
df<- read_csv(file.path(dir, "Cox_PH_amniotic_injection_wo_dummy.csv"))
df$sex_M1F2<-factor(df$sex_M1F2, levels = c(1,2))
df$Tx<-factor(df$Tx, levels = unique(df$Tx))
```

univariate cox regression
```{r}
res.cox<-coxph(Surv(time, status)~ sex_M1F2, data = df)
res.cox
res.cox<-coxph(Surv(time, status)~ Tx , data = df)
res.cox
```

cox with multiple covariates (not multivariate)
```{r , include= FALSE}
covariates <-colnames(df)[c(3,6)]
univ_formulas<-sapply(covariates, 
                      function(x) as.formula(paste('Surv(time, status)~',x))
                        )
univ_models<- lapply(univ_formulas, function (x){coxph(x, data = df)
  
}
  )

# Extract data 
univ_results <- lapply(univ_models,
                       function(x){ 
                          x <- summary(x)
                          p.value<-signif(x$wald["pvalue"], digits=2)
                          wald.test<-signif(x$wald["test"], digits=2)
                          beta<-signif(x$coef[1,1], digits=2);#coeficient beta
                          HR <-signif(x$coef[1,2], digits=2);#exp(beta)
                          HR.confint.lower <- signif(x$conf.int[,"lower .95"], 2)
                          HR.confint.upper <- signif(x$conf.int[,"upper .95"],2)
                          HR <- paste0(HR, " (", 
                                       HR.confint.lower, "-", HR.confint.upper, ")")
                          res<-c(beta, HR, wald.test, p.value)
                          names(res)<-c("beta", "HR (95% CI for HR)", "wald.test", 
                                        "p.value")
                          return(res)
                          #return(exp(cbind(coef(x),confint(x))))
                         })
univ_results
#res <- as.data.frame(univ_results, check.names = FALSE)
#as.data.frame(res)
```

multivariate cox regression
```{r}
res.cox1<-coxph(Surv(time, status)~  sex_M1F2, data = df)
res.cox2<-coxph(Surv(time, status)~  Tx, data = df)
summary(res.cox1)
k2<-summary(res.cox2)
Hazard.ratio<-k2$coefficients[,"exp(coef)"]
signif(Hazard.ratio,2)
```

